Transition from forest to agriculture in the Brazilian Amazon from 1985 to 2021

### 2022-11-22 manuscript/manuscript.Rmd
Add text to the abstract.

abstract: |
  A new dataset was created by calculating the time necessary for deforested forests to transition to agriculture in the Brazillian Amazon biome. The new data can be useful in interdiciplinary studies about land cover and land use change in brazil, its drivers and implications. A main inovation is that the dataset links the deforestation year with the year of agriculture establishment, which can provide new information about this process.

>>>>

abstract: |
  Land use and land cover changes in the Amazon biome are a main process that influences many aspects at local, national, and global levels. A large quantity of studies already reliad on land use classification to analyse this process, drivers and impacts. A new dataset was created by calculating the time necessary for deforested forests to transition to agriculture in the Brazillian Amazon biome. The new data can be useful in interdiciplinary studies about land cover and land use change in brazil, its drivers and implications. A main inovation is that the dataset links the deforestation year with the year of agriculture establishment, which can provide new information about this process.

### 2022-11-22 manuscript/manuscript.tex
Add text to the abstract.

\begin{abstract}
A new dataset was created by calculating the time necessary for deforested forests to transition to agriculture in the Brazillian Amazon biome. The new data can be useful in interdiciplinary studies about land cover and land use change in brazil, its drivers and implications. A main inovation is that the dataset links the deforestation year with the year of agriculture establishment, which can provide new information about this process.
\end{abstract}

>>>>

\begin{abstract}
Land use and land cover changes in the Amazon biome are a main process that influences many aspects at local, national, and global levels. A large quantity of studies already reliad on land use classification to analyse this process, drivers and impacts. A new dataset was created by calculating the time necessary for deforested forests to transition to agriculture in the Brazillian Amazon biome. The new data can be useful in interdiciplinary studies about land cover and land use change in brazil, its drivers and implications. A main inovation is that the dataset links the deforestation year with the year of agriculture establishment, which can provide new information about this process.
\end{abstract}
